# Dynamic Panel Data Model

## Introduction

Linear dynamic panel data models account for dynamics and unobserved individual-specific heterogeneity. Due to the presence of lagged dependent variables, applying ordinary least squares including individual-specific dummy variables is inconsistent.

## Model Specification

$$y_{it}=\alpha y_{i,t-1}+\beta x_{i,t}+u_{i,t}$$
$$u_{i,t}=\eta_i+\varepsilon_{i,t}$$
$$y_{it}=\alpha y_{i,t-1}+\beta x_{i,t}+\eta_i+\varepsilon_{i,t}$$

First Difference to elliminate $\eta_i$

$$\Delta y_{it}=\alpha \Delta y_{i,t-1}+\beta \Delta x_{i,t}+\Delta \varepsilon_{i,t}$$

## R implementation for Arrelano and Bond (1991)

n=140 firms
T=9

```{r}

library(plm)
library(pdynmc)

# Load Data
data(EmplUK, package = "plm")
dat <- EmplUK
dat[,c(4:7)] <- log(dat[,c(4:7)])
names(dat)[4:7] <- c("n", "w", "k", "ys")
data.info(dat,i.name = "firm",t.name = "year") 
```

```{r}
strucUPD.plot(dat,i.name = "firm",t.name = "year")
```
## Estimation

```{r}
m1 <- pdynmc(
    dat = dat,
    varname.i = "firm",
    varname.t = "year",
    use.mc.diff = TRUE, 
    use.mc.lev = FALSE, 
    use.mc.nonlin = FALSE,
    include.y = TRUE,
    varname.y = "n",
    lagTerms.y = 2,
    fur.con = TRUE,
    fur.con.diff = TRUE,
    fur.con.lev = FALSE,
    varname.reg.fur = c("w", "k", "ys"),
    lagTerms.reg.fur = c(1,2,2),
    include.dum = TRUE,
    dum.diff = TRUE,
    dum.lev = FALSE,
    varname.dum = "year",
    w.mat = "iid.err",
    std.err = "corrected",
    estimation = "twostep",
    opt.meth = "none"
)
summary(m1)
```

## Hypotheses Testing

### Arrelano Bond Serial Correlation

```{r}
mtest.fct(m1,t.order = 2) 
```
The test does not reject the null hypothesis at any plausible significance level and provides no indication that the model specification might be inadequate.

### Hansen J-test

```{r}
jtest.fct(m1)
```

### Wald Test

```{r}
wald.fct(m1,param = "all")
```

